---
title: "p8105_hw1_cm3928"
author: "Clement Mugenzi"
date: "9/14/2019"
output: github_document
---
# Question 1

## First Part

```{r Creating a Dataframe, include=TRUE}
library(tidyverse)

hw_df <- tibble(
  rad_sample = rnorm(8),
  log_vec = rad_sample > 0,
  char_vec = "12345678",
  vec_factor = factor(c("40209383", "12544478",
                        "08327492", "40209383",
                        "12544478", "08327492",
                        "40209383", "12544478"))
)

mean_samp = mean(pull(hw_df, rad_sample))
mean_samp
mean_log = mean(pull(hw_df, log_vec))
mean_char = mean(pull(hw_df, char_vec))
mean_fac = mean(pull(hw_df, vec_factor))
```

A warning message is generated because I am trying to calculate the mean of character variables and that is not possible.
I am going to have to convert some (if not all) my variables to numeric in order to obtain their respective mean. 

Below I will convert the logical, character, and factor variables to numeric using the 'as.numeric' function.

```{r, eval=FALSE}
as.numeric(pull(hw_df, log_vec))
as.numeric(pull(hw_df, char_vec))
as.numeric(pull(hw_df, vec_factor))
```

## What happens?

* When as.numeric is applied on the logical variable, I get zeros and ones back, which represents FALSE and TRUE respectively. Therefore, the as.numeric basically converted characters into numbers. And when the mean function is applied on this new logical variable, I get 0.375 as its mean (this mean is subjected to change every time this code is ran since we are dealing with a random sample).

* Secondly, when as.numeric is applied on the char_vec, the result is eight identical numbers since variables in a dataframe have to be of the same lenght. Therefore, since the character variable was inside quotes, the as.numeric fucntion produces real numbers (without quotes) but this function dows not convert this character variable to numeric.

* Third, when as.numeric is applied on the vec_factor, the result are numbers from one to three which represents the three levels and their distribution in the factor variable. Again as.numeric does not change this factor variable to numeric. 

## Why?

The reason why we could not determine the mean of the last two variables is because they are neither numeric not are they logical.

Yes, this explain why we could only find the mean of the random sample and logical variable (as they are numeric and logical) but not the mean for character and factor variables.

## Second Part

In this section, I will perform three different tasks in the same code chunk. 

1. First, I will convert the logical vector to numeric, and multiply the random sample by the result
2. I will convert the logical vector to a factor, and multiply the random sample by the result
3. Third, I will convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r, include=TRUE}
# (1)
log_as_num <- as.numeric(pull(hw_df, log_vec))
log_as_num
x <- log_as_num
y <- rnorm(8)
x * y # Where x is the converted logical variable and y the random sample.

# (2)
log_as_fac <- as.factor(log_as_num)
t <- log_as_fac
t * y

# (3)
log_to_num <- as.numeric(log_as_fac)
d <- log_to_num
d * y # where d is the converted logical factor and y the random sample.
```

# Question 2


