---
title: "p8105_hw1_cm3928"
author: "Clement Mugenzi"
date: "9/14/2019"
output: github_document
---
# Question 1

## Creating a Dataframe 


```{r setup, include=TRUE}
library(tidyverse)

hw_df <- tibble(
  rad_sample = rnorm(8),
  log_vec = rad_sample > 0,
  char_vec = "12345678",
  vec_factor = factor(c("40209383", "12544478",
                        "08327492", "40209383",
                        "12544478", "08327492",
                        "40209383", "12544478"))
)

mean_samp = mean(pull(hw_df, rad_sample))
mean_log = mean(pull(hw_df, log_vec))
mean_char = mean(pull(hw_df, char_vec))
mean_fac = mean(pull(hw_df, vec_factor))
```

A warning message is generated because I am trying to calculate the mean of character variables and that is not possible.
I am going to have to convert some (if not all) my variables to numeric in order to obtain their respective mean. 

Below I will convert the logical, character, and factor variables to numeric using the 'as.numeric' function.

```{r, eval=FALSE}
as.numeric(pull(hw_df, log_vec))
as.numeric(pull(hw_df, char_vec))
as.numeric(pull(hw_df, vec_factor))
```






